**Machine learning identifies unique taxa differentiating proximal and distal

### 2017-05-10 submission/manuscript.Rmd
oncogenic otus updated with results
discussion updates

### exit comparison models? other findings- fuso etc

@@

Discussion of differentially abundant OTUs, how they fit the ecological regions of the gut (schematic?)

@@

Fuso found on the right side?

@@

-what's next? cancer associated OTUs on one side or the other, compare to previous studies. But really to understand what's going on in the various regions of the gut we need more information than just 16S

>>>>

### exit comparison models?

##draft of oncogenic OTU paragraph, this may go in results or discussion

Some of the healthy patients have Fusobacterium OTUs. The most frequent sequence associated wtih the _Fusobacterium_ genus was OTU179, which BLASTs to _Fusobacterium nucleatum subspecies animalis_. It is the only OTU to align with a nucleatum strain- the only species of _Fusobacterium_ known to have oncogenic properties and be found on the surfaces of colorectal cancer tumors. ((cite joe and niels work somewhere in here, maybe in the discussion?)). The _Fusobacterium_ positive samples were located on the right and left mucosa and ranged up to 1% of the sample. ((Table or something?)). OTU00152 is _Porphyromonas_ and the most frequent sequence in that OTU aligns to _Porphyromonas asacharolytica_, another bacterium commonly detected and isolated from colorectal tumors. OTU152 was only detected on the left mucosa, and in fact was one of the OTUs the classification model identified as separating left and right sides. Samples that were positive for _P. asacharolytica_ ranged in abundances from 0.01% - 16%. Finally, another commonly cancer-associated species, _Parvimonas micra_ was identified to be most similar to OTU248. Only 4 individuals had this bacteria present in their colons, three in the left mucosa and one in the right mucosa.

@@

Discussion of differentially abundant OTUs, how they fit the ecological regions of the gut (schematic?)
some of the very high OTUs BLAST to stool residents, like that one bacteriodes (OTU20)

@@

We detected _F. nucleatum_ and _P. asacharolytica_ in 7 and 5 of our patients, respectively. These bacteria have been shown to be predictive of colorectal cancer in humans (cite Niel). Interestingly, while _F. nucleatum_ was found on both sides of the colon, _P. asacharolytica_ was only detected in the left mucosa. Not much is known about the distribution of _P. asacharolytica_ but given its documented anaerobic characteristics, it might not be surprising that it resides in the less-oygen-rich left bowel (cite something). In studies examining bacteria on colorectal cancer tumors, _F. nucleatum_ is more commonly detected on right-sided tumors, and distribution of _F. nucleatum_ decreases along the colon to rectum (cite Mima 2016). Of the (8) individuals positive for _F. nucleatum_ in this study, the bacteria was spread across the right mucosa, left lumena and left mucosa. That said, in a previous study of 1,102 colorectal cancer cases, only 138 (11%) of them contained detectable _F. nucleatum_ at all (Mima 2016).

Fuso found on the right side? discussion about cancer-specific OTUS
cant pull out ETBF or pks+ ecoli with 16S
found fuso and porpyhromonas, but these are healthy people
what is rate of colonization with these bugs in healthy in literature?
of course presence does not precede cancer or IBD necessarily

@@

-what's next?  But really to understand what's going on in the various regions of the gut we need more information than just 16S
